\documentclass[12pt]{amsart}
\usepackage{amsmath,amsthm,amssymb,amsfonts,enumerate,mymath,tikz-cd,fancyhdr}
\openup 5pt
\author{Blake Farman\\University of South Carolina}
\title{Math 170\\ Exam 01}
\date{March 3, 2016}
\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage[margin=1in]{geometry}

\renewcommand{\qedsymbol}{}

\begin{document}
\maketitle

\begin{center}
  \fbox{\fbox{\parbox{5.5in}{\centering
        Answer the questions in the spaces provided on the
        question sheets and turn them in at the end of the class period.
        If you require extra space, use the back of the page and indicate that you have done so.
        
        Unless otherwise stated, all supporting work is required.
        Unsupported or otherwise mysterious answers will {\bf not receive credit.}}}}
\end{center}

\vspace{0.2in}
\makebox[\textwidth]{Name:\enspace\hrulefill}
\vspace{0.2in}

$$
\begin{array}{|c|c|c|}
  \hline
  \text{Problem} & \text{Points Earned} & \text{Points Possible}\\
  \hline
  1 & & 10\\
  \hline
  2 & & 20\\
  \hline
  3 & & 12\\
  \hline
  4 & & 18\\
  \hline
  5 & & 20 \\
  \hline
  6 & & 20 \\
  \hline
  \text{Bonus} & & 10\\
  \hline
  \text{Total} & & 100\\
  \hline
\end{array}
$$

\theoremstyle{plain}
\newtheorem{thm}{}
\newtheorem{lem}{Lemma}
\theoremstyle{definition}
\newtheorem{defn}{Definition}

\newpage

%\section{Problems}

\begin{thm}[10 Points]\label{ex1}
  Let $S$ be the set of all students at the University of South Carolina.
  Let $A$ be the subset of all students not taking Math 170 this semester.
  Let $B$ be the subset of all students not majoring in business.
  \begin{enumerate}[(a)]
  \item
    In words, what does the set $A \cup B$ represent?
    \vspace{1.5in}
  \item
    In words, what does the set $A \cap B$ represent?
    \vspace{1.5in}
  \item
    In words, what do the sets $S \setminus A$ and $S \setminus B$ represent?
    \vspace{1.5in}
  \item
    In words, what does the set $\left(S \setminus A\right) \cap \left(S \setminus B\right)$ represent?
    \vspace{1.5in}
  \item
    In words, what does the set $\left(S \setminus A\right) \cup \left(S \setminus B\right)$ represent?
  \end{enumerate}
  
\end{thm}

\newpage
\begin{thm}[20 Points]\label{ex2}
  A bag contains four red marbles, two green marbles, one lavender marble, one yellow marble, and one orange marble.
  The marbles are all distinguishable.
  \begin{enumerate}[(a)]
  \item
    How many sets of four marbles include none of the red ones?
    \vspace{4in}
  \item
    How many sets of four marbles include exactly one red marble?
  \end{enumerate}  
\end{thm}

\newpage

\begin{thm}[12 Points]\label{ex3}
  How many two letter sequences can be made using the four letters 
  \begin{center}r, e, a, d?\end{center}
\end{thm}

\newpage

\noindent Let $U = \{A, B, C, D, E, F\}$.
Let 
$X = \{A,C,E\},$
$Y = \{B, C, D, E\},\, \text{and}$
$Z = \{C, D\}.$
Use these sets to answer problems \ref{ex4} and \ref{ex5}.
\begin{thm}[18 Points]\label{ex4}
  Compute
  \begin{enumerate}[(a)]
  \item
    $X \cap Y$,
    \vspace{2.5in}
  \item
    $X \cup Z$,
    \vspace{2.5in}
  \item
    The complement of $Z$ in $U$, $U \setminus Z$.
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}[20 Points]\label{ex5}
  \begin{enumerate}[(a)]
  \item
    What is the cardinality of $X \times Z$?
    \vspace{4in}
  \item
    What is the cardinality of $Y \cup Z$?
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}[20 Points]\label{ex9}
  Use a truth table to prove the following logical equivalences.
  \begin{enumerate}[(a)]
  \item
    $$p \implies q \equiv \neg q \implies \neg p.$$
    \vspace{4in}
  \item
    $$p \wedge (p \implies q) \equiv p \wedge q.$$
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}[Bonus - 10 Points]\label{bonus}
  Write out either form of Disjunctive Syllogism symbolically.
  State the conditions for an argument to be valid and then prove that Disjunctive Syllogism is a valid argument.
  Can you give an example of how Disjunctive Syllogism is used?
\end{thm}
\end{document}
