\documentclass[12pt]{amsart}
\usepackage{amsmath}
\usepackage{enumerate}
\openup 5pt

\author[Blake Farman]{Blake Farman\\University of South Carolina}
\title[Quadratic Worksheet]{Math 111\\Quadratics Worksheet}
\date{November 28, 2017}

\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage[margin=1in]{geometry}

\theoremstyle{definition}
\newtheorem{thm}{}
\renewcommand{\qedsymbol}{}

\begin{document}
\maketitle

\vspace{0.2in}
\makebox[\textwidth]{Name:\enspace\hrulefill}
\vspace{0.2in}

Let $f(x) = -3x^2 + 6x + 9$.
Use this function to answer questions Problems~\ref{problem: vertex form}-\ref{problem: graphs}.
\begin{thm}\label{problem: vertex form}
    Write $f(x)$ in vertex form.
    \vspace{2in}
\end{thm}

\begin{thm}\label{problem: functions and transformations}
    List in order the functions and transformations to get from the graph of $y = x^2$ to the graph of $y = f(x)$.
\end{thm}

\newpage

\begin{thm}\label{problem: graphs}
  Starting from the graph of $y = x^2$ and ending at the graph of $y = f(x)$, sketch a graph of each of the functions, in order, from your answer to Problem~\ref{problem: functions and transformations}.
  Label the vertex and $y$-intercept on each of your graphs.
\end{thm}

\newpage

\begin{thm}\label{problem: quick and dirty}
  \begin{enumerate}[(a)]
  \item\label{quick and dirty: roots}
    Solve the equation
    $$x^2 - 2x - 8 = 0$$
    for $x$.
    \vspace{2in}
  \item\label{quick and dirty: y-intercept}
    Find the $(x,y)$-coordinates of the $y$-intercept of
    $$y = x^2 - 2x - 8.$$
    \vspace{2in}
  \item\label{quick and dirty: vertex}
    Find the $(x,y)$-coordinates of the vertex of
    $$y = x^2 - 2x - 8.$$
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}\label{problem: graph quick and dirty}
  Use your answers to Problem~\ref{problem: quick and dirty} to sketch a graph of
  $$y = x^2 - 2x - 8 .$$
  Label the $y$-intercept, $x$-intercept(s), and the vertex.
\end{thm}

\newpage
Bob tosses a ball straight up in the air.
When he releases the ball, it leaves his hand at a velocity of 96 feet/sec.
The height of the ball relative to Bob's hand after $t$ seconds can be modeled by the function
$$h(t) = -32t^2 + 96t.$$
Use this model to answer the following Problems.
\begin{thm}\label{problem: kinematics graph}
  Sketch a graph of this function.
  Make sure that your graph is appropriate for this model.
\end{thm}

\newpage

\begin{thm}\label{problem: maximum}
  Use your answer from the previous problem to answer the following questions.
  \begin{enumerate}[(a)]
  \item
    After how many seconds does the ball reach its maximum height?
    \vspace{2in}
  \item
    What is the maximum height attained by the ball?
    \vspace{2in}
  \item
    After how many seconds does the ball return to Bob's hand?
  \end{enumerate}
\end{thm}

\end{document}
