\documentclass[12pt]{amsart}
\usepackage{amsmath,amsthm,amssymb,amsfonts,enumerate,mymath,tikz-cd,fancyhdr}
\openup 5pt
\author{Blake Farman\\University of South Carolina}
\title{Math 116: Final Exam}
\date{December 9, 2013}
\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage[margin=1in]{geometry}

\renewcommand{\qedsymbol}{}

\begin{document}
\maketitle

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
Answer the questions in the spaces provided on the
question sheets and turn them in at the end of the class period. 
Unless otherwise stated, all supporting work is required.
You may {\it not} use any calculators.}}}
\end{center}

\vspace{0.2in}
\makebox[\textwidth]{Name:\enspace\hrulefill}
\vspace{0.2in}

\theoremstyle{plain}
\newtheorem{thm}{}
\newtheorem{lem}{Lemma}
\theoremstyle{definition}
\newtheorem{defn}{Definition}

\begin{thm}[10 Points]\label{ex1}
  Find the period, frequency, and amplitude of $y = 3\sin(4x) - 1$, then graph one period.
\end{thm}

\newpage

\begin{thm}[10 Points]
	Graph the function $f(x) = -3x^2 - 6x + 15$.
	Label the $x$-intercepts, $y$-intercept, and the vertex.
	\vspace{3.5in}
\end{thm}

\begin{thm}[10 Points]\label{ex3}
  Let $f(x) = 2x^2$ and $g(x) = x-1$.
  \begin{enumerate}[(a)]
  \item
    Compute $(f \circ g)(x)$.
    \vspace{2in}
  \item
    Compute $(g \circ f)(x)$.
    \vspace{2in}
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}[10 Points]
	Find all the solutions (real and complex) to the equation 
	$$x^4 - x = 0.$$
	\vspace{3in}
\end{thm}

\begin{thm}[10 Points]
	Show that $$\sin^2\left(\frac{1}{2}\arccos(x)\right) = \frac{1- x}{2}.$$
\end{thm}

\newpage

\begin{thm}[10 Points]
	Consider the polynomial $p(x) = x^3 - 6x^2 + 11x - 6$.
	Observe that 
	$$p(1) = 1 - 6 + 11 - 6 = 12 - 12 = 0.$$
	Use this information to factor $p(x)$ completely.
	\vspace{3.5in}
\end{thm}

\begin{thm}[10 Points]
	Recall that $\sin(\theta \pm \phi) = \sin(\theta)\cos(\phi) \pm \sin(\phi)\cos(\theta)$.
	Use this identity to show that
	$$\sin\left(\frac{\pi}{6}\right) = \cos\left(\frac{\pi}{3}\right).$$
\end{thm}

\newpage

\begin{thm}[10 Points]
	Simplify 
	$$\frac{x^2 - 3}{x - \sqrt{3}}$$
	by rationalizing the denominator.
	\vspace{3in}
\end{thm}

\begin{thm}[10 Points]\label{ex4}
  Determine whether $f(x) = \log_2(x + 1)$ is invertible.
  If it is, then compute the inverse.  
  Otherwise, explain why it does not have an inverse.
\end{thm}

\newpage

\begin{thm}[10 Points]\label{ex5}
  Solve the following equations for $x$.
  \begin{enumerate}[(a)]
  \item
    $$\log_5(x + 1) - \log_5(x - 1) = 2$$
    \vspace{3.5in}
  \item
    $$5^{-4x} = 25^2 \cdot 5^{x^2}$$
  \end{enumerate}
\end{thm}
\end{document}
