\documentclass[12pt]{amsart}
\usepackage{amsmath,amsthm,amssymb,amsfonts,enumerate,mymath,tikz-cd,fancyhdr}
\openup 5pt
\author{Blake Farman\\University of South Carolina}
\title{Math 111: Exam 02}
\date{June 7, 2013}
\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage[margin=1in]{geometry}

\renewcommand{\qedsymbol}{}

\begin{document}
\maketitle

\begin{center}
  \fbox{\fbox{\parbox{5.5in}{\centering
        Answer the questions in the spaces provided on the
        question sheets and turn them in at the end of the class period. 
        Unless otherwise stated, all supporting work is required.}}}
\end{center}

\vspace{0.2in}
\makebox[\textwidth]{Name:\enspace\hrulefill}
\vspace{0.2in}

\theoremstyle{plain}
\newtheorem{thm}{}
\newtheorem{lem}{Lemma}
\theoremstyle{definition}
\newtheorem{defn}{Definition}

\section{Definitions}
\begin{thm}[4 Points]\label{ex1}
  \begin{enumerate}[(a)]
  \item
    State the Point-Slope form of a line passing through the point $(x_1, y_1)$ with slope $m$.
    \vspace{1in}
  \item
    State the Slope-Intercept form of a line with slope $m$ and $y$-intercept $b$.
    \vspace{1in}
  \end{enumerate}
\end{thm}

\begin{thm}[6 Points]\label{ex2}
  Let $f(x)$ be a function.
  State the average rate of change of $f$ between $x = a$ and $x = b$.
\end{thm}

\newpage

\begin{thm}[5 Points]\label{ex3}
  State the growth rate formula for a function $f(x)$.
  \vspace{1in}
\end{thm}

\begin{thm}[3 Points]\label{ex4}
  \begin{enumerate}[(a)]
  \item
    State the general form of an exponential function.
    \vspace{1in}
    \item
      When does such a function model exponential growth?
      \vspace{1in}
    \item
      When does such a function model exponential decay?
      \vspace{1in}
  \end{enumerate}
\end{thm}

\begin{thm}[2 Points]
  Consider the two lines $f(x) = m_1x + b_2$ an $g(x) = m_2x + b_2$.
  \begin{enumerate}[(a)]
  \item
    When are $f$ and $g$ parallel?
    \vspace{1in}
  \item
    When are $f$ and $g$ perpendicular?
    \vspace{1in}
  \end{enumerate}
\end{thm}

\newpage
\section{Problems}

\begin{thm}[16 Points]\label{ex5}
  In the following problems, use the given information to find the equation of the line in slope-intercept form.
  \begin{enumerate}[(a)]
  \item
    The line passing through the points $(2,5)$ and $(4,13)$.
    \vspace{1in}
  \item
    The line passing through the point $(-3, 3)$ and parallel to the line $2y - 4x = 20$.
    \vspace{1in}
  \item
    The line passing through the origin (that is, the point $(0,0)$) and perpendicular to the line $2y - 4x = 20$.
    \vspace{1in}
  \end{enumerate}
  \vspace{1in}
\end{thm}


\begin{thm}[16 Points]\label{ex10}
  Consider the two lines $f(x) = 4x + 3$ and $g(x) = x + 12$.
  Find the point (that is, the $(x,y)$ pair) where these two lines intersect.
  \vspace{2in}
\end{thm}

\newpage

\begin{thm}[16 Points]\label{ex9}
  Let $f(x) = x^2$.
  \begin{enumerate}[(a)]
  \item
    Compute the average rate of change for $f$ between $x = 2$ and $x = 5$.
    \vspace{1in}
  \item
    Give the Point-Slope form of a line that passes through $(2, f(2))$ and $(5, f(5))$.
    \vspace{1in}
  \item
    Give the Slope-Intercept form of a line that passes through $(2, f(2))$ and $(5, f(5))$.
    \vspace{1in}
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}[16 Points]\label{ex7}
  Alice is hosting an event.  She is renting a facility, which costs $\$300$, and providing refreshments, which cost $\$4$ per guest.
  \begin{enumerate}[(a)]
  \item
    Find a function, $C$, that models the total cost of the event if $x$ people attend.
    \vspace{1in}
  \item
    Sketch a graph of $C$.
    \vspace{2in}
  \item
    Evaluate $C(10)$ and $C(15)$.  What do these numbers represent?
    \vspace{1in}
  \item
    If the total cost for the event was $400$, how many people attended?
    \vspace{1in}
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}[16 Points]
  A population of size $25$ grows by $20\%$ every day.
  \begin{enumerate}[(a)]
  \item
    Give the growth factor for this population.
    \vspace{1in}
  \item
    Give an exponential model for the size of the population after $t$ days.
    \vspace{1.5in}
  \item
    Determine the size of the population after 2 days.  [Hint: Express the growth factor as a ratio, rather than a decimal, and this will be easy to compute.]
    \vspace{1.5in}
  \end{enumerate}
\end{thm}

\begin{thm}[Bonus - 10 Points]\label{bonus}
  Let $f(x) = m_1x + b_1$ and $g(x) = m_2x + b_2$.
  Using $f$ and $g$, derive the general formula for the intersection of two lines.
  Use this to explain why two parallel lines never intersect.
\end{thm}
\end{document}
