\documentclass[12pt]{amsart}
\usepackage{amsmath,amsthm,amssymb,amsfonts,enumerate,mymath,tikz-cd,fancyhdr}
\openup 5pt
\author{Blake Farman\\University of South Carolina}
\title{Math 115\\ Exam 02}
\date{October 15, 2014}
\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage[margin=1in]{geometry}

\renewcommand{\qedsymbol}{}

\begin{document}
\maketitle

\begin{center}
  \fbox{\fbox{\parbox{5.5in}{\centering
        Answer the questions in the spaces provided on the
        question sheets and turn them in at the end of the class period. 
        Unless otherwise stated, all supporting work is required.
        It is advised, although not required, that you check your answers.
        You may {\bf not} use any calculators.}}}
\end{center}

\vspace{0.2in}
\makebox[\textwidth]{Name:\enspace\hrulefill}
\vspace{0.2in}

\theoremstyle{plain}
\newtheorem{thm}{}
\newtheorem{lem}{Lemma}
\theoremstyle{definition}
\newtheorem{defn}{Definition}

$$
\begin{array}{|c|c|c|}
  \hline
  \text{Problem} & \text{Points Earned} & \text{Points Possible}\\
  \hline
  1 & & 20\\
  \hline
  2 & & 20\\
  \hline
  3 & & 20\\
  \hline
  4 & & 20\\
  \hline
  5 & & 20\\
  \hline
  \text{Bonus} & & 10\\
  \hline
  \text{Total} & & 100\\
  \hline
\end{array}
$$

\newpage

\section{Problems}

\begin{thm}
  Graph the function
  $$f(x) = \left\{
  \begin{array}{cc}
    -3x + 1 & \text{if}\ x > 0,\\
    2x - 3 & \text{if}\ x \leq 0.
  \end{array}
  \right.
  $$
\end{thm}

\newpage
\begin{thm}
  Let $f(x) = 3x^2 + 6x + 2$.
  \begin{enumerate}[(a)]
  \item
    Find the solutions to $f(x) = 0$.
    \vspace{2in}
  \item
    Write $f(x)$ in vertex form.
    \vspace{2in}
  \item
    Find the coordinates of the $y$-intercept for $f(x)$.
    \vspace{2in}
  \item
    Use parts (a)-(c) to sketch a graph of $f(x)$.
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}
  Find and simplify the difference quotient for $f(x) = x^2 - x$.
\end{thm}

\newpage

\begin{thm}
  Let $f(x) = 3x - 1$ and $g(x) = x^2 + 1$.
  \begin{enumerate}[(a)]
  \item
    Compute the composition $(f \circ g)(x)$
    \vspace{4in}
  \item
    Compute the composition $(g \circ f)(x)$
  \end{enumerate}
\end{thm}

\newpage

\begin{thm}
  Find the inverse of the function
  $$f(x) = 2x + 1.$$
\end{thm}

\newpage

\begin{thm}[Bonus]
  Let $f(x) = \sqrt{1 - x^2}$.  Determine the domain of this function.
  Is this function invertible?
  If so, compute its inverse.
  %[Hint: Compute the composition $f \circ f (x)$]
\end{thm}
\end{document}
