\documentclass[10pt]{amsart}
\usepackage{style}

\title{Related Rates}
\date{September 17, 2018}
\author{Blake Farman}
\address{Lafayette College}

\begin{document}
\maketitle

\makenameslot

\begin{thm}
  Gas is escaping a spherical balloon at the rate of 4 \(cm^3\) per minute.  How fast is the surface area shrinking when the radius is 24 \(cm\)?  For a sphere, \(\displaystyle{V=\frac{4}{3}\pi r^3}\) and \(\displaystyle{S=4\pi r^2}\) where \(V\) is volume, \(S\) is surface area and \(r\) is the radius of the balloon.
\end{thm}

\newpage
\begin{thm}
  The top of a ladder slides down a vertical wall at a rate of 0.15 meters/second.
  At the moment when the bottom of the ladder is 3 meters from the wall, it slides away from the wall at a rate of 0.2 meters/second.
  How long is the ladder?
\end{thm}

\vspace{3in}

\begin{thm}
  A plane flying with a constant speed of 300 kilometers/hour passes over a ground radar station at an altitude of 1 kilometer and climbs at an angle of \(30^\circ\).
  At what rate is the distance from the plane to the radar station increasing a minute later?\\
  (Hint: Use the law of cosines)
\end{thm}
\newpage
\begin{thm}
  Two cars start moving from the same pont.
  One travels south at 60 mi/h and the other travels west at 25 mi/h.
  At what rate is the distance between the cars increasing two hours later?
\end{thm}

\vspace{3in}
\begin{thm}
  A street light is mounted at the top of a 15-ft-tall pole.
  A man 6 ft tall walks away from the pole with a speed of 5 ft/s along a straight path.
  How fast is the tip of his shadow moving when he is 40 ft from the pole?\\
  (Hint: The length of the shadow is measured from the person to the tip of the shadow; the rate at which the tip of the shadow is moving is measured from the pole to the tip of the shadow.)
\end{thm}
\end{document}

