\documentclass[12pt]{amsart}
\usepackage{amsmath,enumerate,commath,tikz}
\usetikzlibrary{angles,quotes}
\openup 5pt
\author[Blake Farman]{Blake Farman\\University of South Carolina}
\title[Exam 03]{Math 142: Exam 03}
\date{April 17, 2018}
\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage[margin=1in]{geometry}

\renewcommand{\qedsymbol}{}

\begin{document}
\maketitle

\begin{center}
  \fbox{\fbox{\parbox{5.5in}{\centering
        Answer the questions in the spaces provided on the
        question sheets and turn them in at the end of the class period.

        Unless otherwise stated, all supporting work is required.
        Unsupported or otherwise mysterious answers will \textbf{not receive credit.}
        
        You may \textbf{not} use a calculator or any other electronic device, including cell phones, smart watches, etc.
        By writing your name on the line below, you indicate that you have read and understand these directions.


        It is advised, although not required, that you check your answers.}}}
\end{center}

\vspace{0.2in}
\makebox[\textwidth]{Name:\enspace\hrulefill}
\vspace{0.2in}

\theoremstyle{definition}
\newtheorem{thm}{}
\renewcommand{\qedsymbol}{}

\[
\begin{array}{|c|c|c|}
  \hline
  \text{Problem} & \text{Points Earned} & \text{Points Possible}\\
  \hline
  1 & & 25\\
  \hline
  2 & & 25\\
  \hline
  3 & & 25\\
  \hline
  4 & & 25\\
  \hline
  \text{Exam 1 Bonus} & & -\\
  \hline
  \text{Exam 2 Bonus} & & -\\
  \hline
  \text{Total} & & 100\\
  \hline
\end{array}
\]

\newpage

\section{Problems}

\begin{thm}[25 Points]
  Find the radius and interval of convergence for the power series
  \[\sum_{n = 0}^\infty \frac{3^nx^n}{n!}.\]
\end{thm}

\vspace{3in}

\begin{thm}[25 Points]
  Find the Maclaurin series for the function
  \[f(x) = \frac{1}{(1-x)^3}.\]
\end{thm}

\newpage
\begin{thm}[25 Points]
  Find the Maclaurin series for \(x\ln(1 + 2x)\).
\end{thm}

\newpage


\begin{thm}[25 Points]
  Find the Maclaurin series for
  \[\ln\left(\frac{1 + x}{1 - x}\right)\]
\end{thm}

\newpage

\begin{thm}[Bonus - Exam 1]
  Decide whether 
  \[\int_2^\infty \frac{\dif x}{x^2 - 1}\]
  converges or diverges.
  If it converges, find the value of the integral.
\end{thm}

\vspace{3in}
\begin{thm}[Bonus - Exam 2]
  Determine whether the series
  \[\sum_{n = 1}^\infty (-1)^n\frac{2n}{4n^2 + 1}\]
  converges conditionally, converges absolutely, or diverges.
\end{thm}

\end{document}
